Sequential rank agreement methods for comparison of ranked lists

### 2015-04-22 latex/paper.Rnw
Initial changepoint analysis

\begin{figure}[tb]
\begin{center}
<<fig=TRUE,echo=FALSE>>=
ysize <- 1000
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
## 
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

bcolor <- makeTransparent("lightblue", alpha=80)
bcolor2 <- makeTransparent("red", alpha=80)

@@

@@

>>>>

\begin{figure}[tb]
\begin{center}
<<fig=TRUE,echo=FALSE>>=
ysize <- 1000
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
## 
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=200))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

bcolor <- makeTransparent("lightblue", alpha=80)
bcolor2 <- makeTransparent("red", alpha=80)
bcolor3 <- makeTransparent("green", alpha=80)

@@

www <- smooth_sra(null3)
polygon(c(1:length(www$lower), rev(1:length(www$lower))),
        c(www$lower, rev(www$upper)),
        col=bcolor3, border=NA)

@@

<<>>=
library(changepoint)
cpt.mean(res)
cpt.mean(res2)
@
